---
title: HITCalculator v1.0
author: M.B. Moran - 18 April 2015
framework: deckjs
highlighter: highlight.js
hitheme    : solarized_light
widgets    : [mathjax, bootstrap, quiz, shiny, interactive]
mode : selfcontained
url:
  lib: ../../libraries
---

## Introducing HITCalculator v1.0!

1. <h3>What this shiny app does:</h3>
   
&nbsp;&nbsp;&nbsp;&nbsp;The HITCalculator is a simple, novel app that does 3 cool things:  
   
&nbsp;&nbsp;&nbsp;&nbsp;a.  Calculates HIT - a Vaccination (or herd immunity) threshold based on 2 user inputs  
&nbsp;&nbsp;&nbsp;&nbsp;b.  Displays a histogram of USA 2013 MMR vaccination rates for Children (19-35 mos)  
&nbsp;&nbsp;&nbsp;&nbsp;c.  Displays 2 USA state maps:   
     
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;(i)  States colored by MMR vaccination level   
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;(ii) States colored to show those which fall below the calculated HIT or at/above the HIT  

---

## 2. Why the app is important

> - Unique! - a similar app does not yet exist in the public domain  
> - Insightful! - a benchmark combined with state vaccination rates provides important context for evaluating potential measles outbreak risks  
> - Graphs! - plots and graphs make it easy to visualize the statistical frequency and regional differences  
> - Simple! - only two imputs required  

---

## 3. Who may be interested?
<h3> Potential Users/Stakeholders:</h3>
```{r echo=FALSE}
plot.new()
par(mar=c(0,0,0,0)+.1)
plot.window(xlim=c(0,3), ylim=c(0,8))
xspline( c(1,1.25,1.75,2), c(6,6,4,4), s=1, lwd=32.8/4.5, border="#0000ff88", lend=1 )
xspline( c(1,1.25,1.75,2), c(5,5,4,4), s=1, lwd=32.8/4.5, border="#0000ff88", lend=1 )
xspline( c(1,1.25,1.75,2), c(4,4,4,4), s=1, lwd=32.8/4.5, border="#0000ff88", lend=1 )
xspline( c(1,1.25,1.75,2), c(3,3,4,4), s=1, lwd=32.8/4.5, border="#0000ff88", lend=1 )
xspline( c(1,1.25,1.75,2), c(2,2,4,4), s=1, lwd=32.8/4.5, border="#0000ff88", lend=1 )
xspline( c(1,1.25,1.75,2), c(1,1,4,4), s=1, lwd=32.8/4.5, border="#0000ff88", lend=1 )

text( rep(0.5, 6), 6:1, c("You","Public Health Officials","Health Providers","Payors/Insurers","Lawmakers","Parents"))

#text( rep(0.75, 6), 6:1, c("You","Public Health Officials","Health Providers","Payors/Insurers","Lawmakers","Parents"))
#text( 2.25, 4, 'HITCalculator App Users')
text( 2.5, 4, 'HITCalculator App Users')

```


--- 


## 4. How it works

A sample calculation of an HIT (Herd Immunity Threshold):

$$V_c=\frac{1-1/R_0}{E}$$

R=Basic Reproduction Number between 12-18 for measles.   
CHOOSE 12

E = Effectiveness of the immunity/vaccine.  
CHOOSE 1.00

```{r, echo=FALSE}
r0<-12
e<-1
Vc<-(1-1/r0)/e *100

cat("Ro entered= ",r0)
cat("E entered= ",e)
cat("Vc calculated= ",Vc," %")

```

--- 


## 5. Example of Plot Output Produced

Here is the shiny app "plot" histogram produced by R code embedded in this slidify presentation:

```{r, echo=FALSE}
library(ggplot2)
setwd("~/Actuarial/Coursera/Data Science/Developing Data Products/Project/myshinyapp")
tf<-read.csv("tab03_antigen_state_2013_MMR_50states.csv",stringsAsFactors = FALSE)
        r0 <- 12
        e <- 1
        hit<-(1-1/r0)/e
        
        dd <- with(density(tf$num), data.frame(x,y))
        g<-ggplot(data=tf, aes(tf$num),environment = environment()) + 
            geom_histogram(breaks=seq(85, 100, by =0.5), 
                           col="red", 
                           aes(fill=..count..))
        
        p <- g + 
            scale_x_continuous(breaks=seq(85,100,by=1),limits=c(85,100),name="MMR Vacination Rate (per 100)")+
            scale_y_continuous(breaks = round(seq(0,max(dd$y)*length(tf$num)+1,by=1),0), name="Number of States") +
            geom_vline(aes(xintercept = hit*100), color = "red", linetype="dashed",show_guide=FALSE) +
            geom_text(aes(99, 7, label="Calculated HIT"),show_guide=FALSE,color="red") +
            geom_text(aes(99, 6.5, label=paste(round(hit*100,digits=1))),show_guide=FALSE,color="red") +
            theme_classic()
        print(p)

```


